\cvsection{Skills}

\textcolor{SlateGrey}{\textbf{Programming Languages}}
\newline

\begin{itemize}
    \item C/C++, Java, Kotlin, Dart, HTML, CSS, JavaScript, Typescript, Sass.
\end{itemize}

\textcolor{SlateGrey}{\textbf{Mobile}}
\newline

\begin{itemize}
    \item \textbf{Android} - Room, Retrofit, Dagger, Hilt, Rx Java, MVC, MVP, MVVM, Clean Architecture.
    \item \textbf{Flutter}
\end{itemize}

		
\textcolor{SlateGrey}{\textbf{Software (Back-end)}}
\newline

\begin{itemize}
    \item \textbf{DevOps} - Docker
    \item \textbf{Full stack} - NodeJs, Express, MongoDB, Mongoose, REST API
    \item\textbf{ Java Full stack} - Spring, Spring-Boot, Spring REST, Hibernate, REST API
    \item \textbf{Front-end} - Angular, React+Redux
\end{itemize}

\textcolor{SlateGrey}{\textbf{Internet Of Things}}
\newline

\begin{itemize}
    \item MQTT Protocol, MQTT broker setup, Mesh Network Design.
    \item Familiar with basic embedded systems concepts.
    \item AWS IOT and Microsoft Azure IOT setup.
\end{itemize}

\textcolor{SlateGrey}{\textbf{Project Management and Soft Skills}}
\newline

\begin{itemize}
    \item Knowledge of Agile methodologies using Scrum and Kanban and JIRA tool.
    \item Technical documentation writing.
    \item Project proposal writing, supervision and monitoring.
\end{itemize}



\cvsection{Education}

\cvevent{M Tech in Software Systems}{BITS Pilani}{2017 -- 2019}{WI LP}


%\cvsection{Achievements}

%\cvachievement{\faTrophy}{Ranking Second in Eurobot 2018}{Eurobot is an international robotics competition organized by planet science held in France in which I led a team for 22 Engineering students and ranked 2nd internationally }
%\cvtag{Leadership} 
%\cvtag{Teamwork}
%\cvtag{Work Ethic}
%\cvtag{Project Management}
%\cvtag{Decision Making}

%\divider

%\cvachievement{\faUsers}{Fablab Manager}{I organized many local competitions and pushed a lot of younger minds to invest their time in learning.}

%\cvtag{Social Skills}
%\cvtag{Motivation}
%\cvtag{Courtesy}


%\cvsection{Languages}



%English \hfill TOEIC (975) 

%\divider

%French \hfill C2 

%\divider

%Arabic \hfill Native 



\cvsection{Other Interests}

\cvtag{Technical Training Instructor}
\cvtag{Open Source Contribution}
\cvtag{E-Learning Content Creation}
\cvtag{Technical Event Organizing}
\cvtag{Project guidance and mentoring}

\cvsection{Declaration}

	{I hereby declare that, the information mentioned above is correct and true to the best of my knowledge and belief.}